---
title: "Smarket weekly"
author: "Abu Imtiaz"
date: "March 4, 2017"
output: md_document
---

```{r}
library(ISLR)
attach(Weekly)
dim(Weekly)
head(Weekly)
pairs(Direction~Lag1+Lag2+Lag3+Lag4+Lag5)
```
Perform Logistic regression with Direction as the response and the five lag cariables plus Volume as predictors.
```{r}
glm.fit<-glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data=Weekly,family=binomial)
summary(glm.fit)
```

Only lag2 seems to be Statistically significant. Now confusion matrix will be formed.
```{r}
glm.probs<-predict(glm.fit,type="response")
glm.pred=rep("Down",1089)
glm.pred[glm.probs>0.5]="Up"
table(glm.pred,Direction)
mean(glm.pred==Direction)
```

The prediction error of logictic regression is about 46%.

Now a logistic regression will be fitted using a training data period from 1990 to 2008 with Lag2 as the only predictor. This model will be used to predict Direction for 2009 to 2010 data.

```{r}
y.train<-Year<2009
D.train<-Weekly[y.train,]
head(D.train)
D.test<-subset(Weekly, Year %in% c(2009,2010))
head(D.test)
glm.fit2<-glm(Direction~Lag2,data=D.train,family=binomial)
glm.probs2<-predict(glm.fit2,D.test,type="response")
dim(D.test)
glm.pred2=rep("Down",104)
glm.pred2[glm.probs2>0.5]="Up"
table(glm.pred2,D.test$Direction)
mean(glm.pred2==D.test$Direction)
```

Now we will use LDA

```{r}
library(MASS)
lda.fit<-lda(Direction~Lag2,data=D.train)
lda.pred<-predict(lda.fit,D.test,type="response")
names(lda.pred)
table(lda.pred$class,D.test$Direction)
mean(lda.pred$class==D.test$Direction)
```

Now we will use QDA
```{r}
qda.fit<-qda(Direction~Lag2,data=D.train)
qda.pred<-predict(qda.fit,D.test,type="response")
names(qda.pred)
table(qda.pred$class,D.test$Direction)
mean(qda.pred$class==D.test$Direction)
```

Now we will use KNN

```{r}
library(class)
D.Direction=Direction[y.train]
head(D.Direction,20)
train.X=as.matrix(Lag2[y.train])
dim(train.X)
test.X=as.matrix(Lag2[!y.train])
dim(test.X)
set.seed(1)
knn.pred=knn(train.X,test.X,D.Direction,k=1)
table(knn.pred,D.test$Direction)
mean(knn.pred==D.test$Direction)
```

Therefore, LDA and Logistic regression provide best results on this data




```
