---
title: "Resampling and classification"
author: "Abu Imtiaz"
date: "March 12, 2017"
output: md_document
---
We will use Default data set from ISLR package. The aim here is to predict which customers will default based on their credit card debt.
```{r}
library(ISLR)
head(Default)
library(ggplot2)
g<-ggplot(Default,aes(balance,income,color=default))
g+geom_point()
```

Now we will divide the dataset into two, one training and one test. And then fit a linear model on the training data using income and balance, obtain a prediction of default status for each individual in the test data and finally compute the validation set error

```{r}
dim(Default)
set.seed(1)
train<-sample(10000,5000)
glm.fit1<-glm(default~balance+income,data=Default[train,],family=binomial)
glm.prob<-predict(glm.fit1,Default[-train,],type="response")
glm.pred<-rep("No",5000)
glm.pred[glm.prob>=0.5]<-"Yes"
table(glm.pred,Default$default[-train])
mean(glm.pred!=Default$default[-train])
```

Now the same process will be repeated including the dummy variable student in the logistic regression model

```{r}
glm.fit2<-glm(default~balance+income+student,data=Default[train,],family=binomial)
glm.prob2<-predict(glm.fit2,Default[-train,],type="response")
glm.pred2<-rep("No",5000)
glm.pred2[glm.prob2>=0.5]<-"Yes"
table(glm.pred2,Default$default[-train])
mean(glm.pred2!=Default$default[-train])
```

There is not much improvement in the test error by including dummy variable in the model

Now we will compute estimates for the standard errors of the income and balance logistic regression coeffients in two different ways (1) bootstrap and (2)the standard formula in glm

```{r,cache=TRUE}
set.seed(1)
#train<-sample(10000,5000)
glm.fit1<-glm(default~balance+income,data=Default,family=binomial)
summary(glm.fit1)$coef

boot.fn<-function(data2,index){
  c<-glm(default~income+balance,data=data2,subset=index,family=binomial)
  coef(c)
}
library(boot)
boot(Default,boot.fn,R=1000)
```
