---
title: "Basic Inferential Data Analysis"
author: "Abu Imtiaz"
date: "February 8, 2017"
output: md_document
---

The dataset in this project desribes the effect of vitamin C on the tooth growth in Guniea Pigs. The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

A data frame with 60 observations on 3 variables.

[,1]	 len	 numeric	 Tooth length
[,2]	 supp	 factor	 Supplement type (VC or OJ).
[,3]	 dose	 numeric	 Dose in milligrams/day


```{r exploratory}
str(ToothGrowth)
summary(ToothGrowth)
library(ggplot2)
g<-ggplot(ToothGrowth,aes(factor(dose),len))
g+geom_boxplot(aes(fill=factor(dose)))+facet_grid(.~supp)
```

Based on this plot it can be concluded that the mean of tooth growth increases with the increase of the dose for both delivery method. This can be verified with hypothesis testing.

###T test comparing dose level 0.5 and 1 mg/day. 
This is independent group t test as the dose is applied to different pigs.

```{r test1}
t1<-subset(ToothGrowth, dose %in% c(0.5,1) & supp %in% c("VC"))
t.test(len~dose, paired = FALSE, var.equal = FALSE, data=t1)
t2<-subset(ToothGrowth, dose %in% c(0.5,1) & supp %in% c("OJ"))
t.test(len~dose, paired = FALSE, var.equal = FALSE, data=t2)
```

Based on the T test it can be concluded that tooth grwoth is higher when using dose 1mg/day for both delivery method. This is also supported by confidence intervals which do not include 0.

###T test comparing dose level 0.5 and 2 mg/day. 
This is independent group t test as the dose is applied to different pigs.

```{r test2}
t3<-subset(ToothGrowth, dose %in% c(0.5,2) & supp %in% c("VC"))
t.test(len~dose, paired = FALSE, var.equal = FALSE, data=t3)
t4<-subset(ToothGrowth, dose %in% c(0.5,2) & supp %in% c("OJ"))
t.test(len~dose, paired = FALSE, var.equal = FALSE, data=t4)
```

Based on the T test it can be concluded that tooth grwoth is higher when using dose 2mg/day for both delivery method. This is also supported by confidence intervals which do not include 0.


###T test comparing dose level 1 and 2 mg/day. 
This is independent group t test as the dose is applied to different pigs.

```{r test3}
t5<-subset(ToothGrowth, dose %in% c(1,2) & supp %in% c("VC"))
t.test(len~dose, paired = FALSE, var.equal = FALSE, data=t5)
t6<-subset(ToothGrowth, dose %in% c(1,2) & supp %in% c("OJ"))
t.test(len~dose, paired = FALSE, var.equal = FALSE, data=t6)
```

Based on the T test it can be concluded that tooth grwoth is higher when using dose 2mg/day for both delivery method. This is also supported by confidence intervals which do not include 0.


###T test comparing delivery method OJ and VC for dose 0.5 mg/day. 
This is independent group t test as the dose is applied to different pigs.

```{r test4}
t7<-subset(ToothGrowth, dose %in% c("0.5"))
t.test(len~supp, paired = FALSE, var.equal = FALSE, data=t7)

```

Based on the T test it can be concluded that tooth grwoth is higher for OJ delivery method using dose 0.5mg/day and the probability that the null hypothesis (the toothe growth is similar) is only 5%. This is also supported by confidence intervals which do not include 0.


###T test comparing delivery method OJ and VC for dose 1 mg/day. 
This is independent group t test as the dose is applied to different pigs.

```{r test5}
t8<-subset(ToothGrowth, dose %in% c("1"))
t.test(len~supp, paired = FALSE, var.equal = FALSE, data=t8)

```

Based on the T test it can be concluded that tooth grwoth is higher for OJ delivery method using dose 1 mg/day and the probability that the null hypothesis (the toothe growth is similar) is only 5%. This is also supported by confidence intervals which do not include 0.

###T test comparing delivery method OJ and VC for dose 2 mg/day. 
This is independent group t test as the dose is applied to different pigs.

```{r test6}
t9<-subset(ToothGrowth, dose %in% c("2"))
t.test(len~supp, paired = FALSE, var.equal = FALSE, data=t9)$conf
t.test(len~supp, paired = FALSE, var.equal = FALSE, data=t9)$p.value
```

The confidance interval does include 0. Therefore, average two growth with OJ and VC delivery method using 2 mg/day dose may not have any difference. The high p value also supports the similarity in average toorh growth with both delivery method when the dose is 2 mg/day.
 